A Standardized Effect Size for Evaluating the Strength of Phylogenetic Signal, and Why Lambda is not Appropriate

### 2020-05-02 Manuscript/SupportingInfo-EKB.Rmd
Balanced analyses up through n = 512 finished.

@@

>>>>

*COPY FIGURES FROM FIGURES FOLDER INTO MANUSCRIPT FOLDER IN ORDER TO KNIT*

@@

*still needs heavy edits*

```{r, echo = FALSE, out.width="95%"}
include_graphics("FigS5.png")

\textbf{Figure S5}. lambda_Z~lambda_input across tree sizes \hfill\break

```{r, echo = FALSE, out.width="95%"}
include_graphics("FigS6.png")

\textbf{Figure S6}. kappa_Z~lambda_input across tree sizes \hfill\break

```{r, echo = FALSE, out.width="95%"}
include_graphics("FigS7.png")

\textbf{Figure S7}. kappa~lambda_input across tree sizes \hfill\break
